\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.15in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome}
\hypersetup{colorlinks=true, urlcolor=blue}
\pagenumbering{gobble}

\begin{document}

\begin{center}
    \textbf{\LARGE Lavantien} \\
    \textit{Software Engineer | AI/LLM, Agentic Workflows, Distributed Systems} \\
    \vspace{2pt}
    \small
    \faEnvelope\ \href{mailto:cariyaputta@gmail.com}{cariyaputta@gmail.com} | 
    \faGithub\ \href{https://github.com/lavantien}{github.com/lavantien} |
    \faLinkedin\ \href{https://linkedin.com/in/lavantien}{linkedin.com/in/lavantien} |
    \faCalendar\ \href{https://cal.com/cariyaputta}{cal.com/cariyaputta} |
    \faPhone\ +1 777 069 420
\end{center}

\section*{Technical Profile}
Seasoned Software Engineer with 7 YoE architecting and implementing distributed/AI systems. Proven track record in delivering complex business solutions. Believer in Apache 2.0 and MIT licenses. Always on top of bleeding-edge research and papers.

\section*{Core Competencies}
\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{AI/LLM}: Pydantic/Lang*/SmolAgents, RAG/GraphRAG, Knowledge Graph, Agentic Pipelines, LLM Evals, Swarm Intelligence.
    \item \textbf{Backend}: C, Go, Python, REST APIs, WebSocket, GRPC, GraphQL, NATS, Postgres, MongoDB, SQLite, Qdrant, FalkorDB.
    \item \textbf{Systems}: Distributed Systems, Edge Computing, Modular Monolith, Fault-Tolerance, Cache/Rate-Limit/Load-Balance.
    \item \textbf{Operations}: Aider, OpenRouter, Playright, Docker/Podman, Compose, CI/CD Pipelines, Ansible, Grafana Stack, AWS/GCP.
\end{itemize}

\section*{Professional Experience}
\textbf{Technical Consultant} | LLM Tournament, Dotfiles, Agentic Workflows, Custom APIs | \textit{(Cariyaputta)} \hfill 11/2022--Present \\
- Designed and developed a portable real-time LLM evaluation platform with great support for prompt engineering. \\
- Developed RAG/GraphRAG pipelines for document processing and monorepo ingestion. \\
- Created specific tools like concurrent scraping and full-text search, Google Takeout to PDF, or Go/Python custom APIs, etc. \\
- Designed and implemented a comprehensive Dotfiles system and optimized developer experience with Linux and Neovim.

\textbf{Software Engineer (L5)} | Order Processing and Payment Platform | \textit{(Confidential Employer)} \hfill 10/2021--11/2022 \\
- Led migration of the Order-Task-Delivery pipeline from Java/PostgreSQL monolith to Go/MongoDB microservices on GCP. \\
- Developed order processing system in Go, handling 500K+ daily transactions involving collaboration with third-party APIs.\\
- Optimized MongoDB aggregation pipelines, reducing query times by 50\% and improving daily transaction throughput by 20\%. \\
- Mentored junior colleagues and wrote extensive technical and operational documentation.

\textbf{Systems Engineer (III)} | Site Monitoring LoRa Mesh, Colorado ETC | \textit{(Confidential Employer)} \hfill 04/2020--09/2021 \\
- Architected distributed edge computing systems using Go and EdgeX, designed finite-state machines for data processing pipelines. \\
- Migrated Java monolith to cloud-native microservices on AWS. \\
- Implemented IoT device communication and observability layers with MQTT, Telegraf, and Grafana Stack.

\textbf{Fullstack Engineer (II)} | White-label Exchange, Generic Trading Platform | \textit{(Confidential Employer)} \hfill 10/2018--03/2020 \\
- Modernized legacy JavaEE platform to modern Spring Boot/Go/Angular TS stack. \\
- Implemented seamless wallet and fraud detection systems for financial transactions.  \\
- Developed real-time HTML canvas games and trading APIs with WebSocket integration.

\textbf{Embedded Engineer (I)} | Micromouse Tunnel-Explorer, Lidar Field-Mapping | \textit{(Confidential Employer)} \hfill 08/2016--09/2018 \\
\textbf{Game Developer (Intern)} | Generic Mobile MOBA | \textit{(Confidential Employer)} \hfill 03/2016--07/2016

\section*{Core Projects}
\textbf{LLM Tournament Platform} (Go/Python/WebSockets) \hfill \href{https://github.com/lavantien/llm-tournament}{\faGithub\ lavantien/llm-tournament} \\
- Real-time evaluation system for benchmarking LLM performance. \\
- Modular architecture supporting multiple evaluation profiles, model sets, and prompt suites. \\
- Integrated dynamic prompt management with Markdown support and minimalist evaluation flow. \\
- Statistical analysis and auto-grading with the multi-tier evaluation system.

\textbf{Enterprise Dotfiles} (Linux/Neovim/Lua) \hfill \href{https://github.com/lavantien/dotfiles}{\faGithub\ lavantien/dotfiles} \\
- Standardized development environment across multiple organizations and platforms. \\
- Integrated 150+ plugins, language servers, and linters with automated updates. \\
- Cross-platform support for Linux/Windows development environments.

\section*{Education \& Community}
\textbf{Computer Engineering, Focus: Robotics and Agentic Systems} | UIT, Vietnam National University. \hfill 20xx--20xx \\
\textbf{Anarchist SWE Open Library} | Curator \& Composer \& Maintainer | \href{https://github.com/lavantien/modern-swe-library}{\faGithub\ lavantien/modern-swe-library} \hfill 2023--2024 \\
\textbf{UIT Sumo Robot League} | 1st Place, Undefeated. \hfill 2017 \\
\textbf{ACM-ICPC Regional} | The earliest team to solve the first problem. \hfill 2016 \\
\textbf{UIT Social Volunteering Team} | Technical Leader: Conduct game development and robotics workshops. \hfill 20xx--20xx

\section*{Interests}
AGI/ASI Alignment, Game Theory, Consciousness (Emergence Mechanisms), Anthropology, Linguistics, Philosophy, Spirituality.

\end{document}
